\begin{recipe}
[ %
    preparationtime = {\unit[???]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{4}},
    calory={???},
]
{Chicken with Balsamic Vinegar and Garlic}

    \graph
    {% pictures%
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[1]{lb}              & Chicken breasts  \\
        \unit[$\frac{3}{4}$]{lb}  & Mushrooms, sliced  \\
        1						  & Onion, diced \\
        \unit[2]{tb}              & Flour  \\
        \unit[2]{tb}              & Olive Oil  \\
        \unit[6]{cloves}          & garlic, minced  \\
        \unit[$\frac{1}{4}$]{cup} & Balsamic Vinegar  \\
        \unit[$\frac{3}{4}$]{cup} & Chicken Broth  \\
        2						  & Bay Leaves \\
        \unit[$\frac{1}{4}$]{tsp} & Dried Thyme (whole) \\
        \unit[1]{tb}              & Butter  \\
        & Salt \\ & pepper \\
    }

    \preparation
    {%
    	\step Combine flour, salt, and pepper in a small bowl, and dredge the chicken breast.
    	\step Heat the olive oil in a large saucepan over medium-high heat.
    	\step Saute the chicken until it is nicely browned on one side, without flipping (about 3 minutes).
    	\step Add the garlic, turn the chicken over, and scatter the mushrooms and onions over the chicken.
    	\step Continue frying, shaking the skillet, and stirring the mushrooms, for about 3 minutes.
    	\step Add vinegar, broth, thyme, and bay leaf. Cover tightly, and simmer over medium-low heat for 10 minutes, turning occasionally.
    	\step Remove the chicken to a plate, and continue simmering the sauce for 7 minutes over medium high heat.
    	\step Mix in the butter, discard the bay leaf, and add the chicken back to the sauce.
    	\step Let the chicken heat for several minutes, then serve hot.
    }

\hint{
This dish goes very well served over pasta (I particularly like penne pasta), with baked asparagus on the side. It's also extremely good when served with a white zinfandel, or other rose wine.
}

\end{recipe}
