\begin{recipe}
[ %
    preparationtime = {\unit[45]{m}},
    bakingtime={\unit[30]{m}},
    bakingtemperature={{350$^{\circ}$ F}},
    portion = {\portion{8}},
    calory={???},
]
{Baked Macaroni and Cheese}

    \ingredients
    {%
    	\unit[8]{tb}					& Unsalted Butter \\
    	\unit[$\frac{1}{2}$]{cup}		& Flour \\
    	\unit[4]{cups}					& Milk \\
    	& salt \\
    	& pepper \\
    	& nutmeg \\
    	\unit[4]{tsp}					& Sherry \\
    	& chives \\
    	2.5								& Onions \\
    	\unit[$\frac{1}{2}$]{tsp}		& Sweet Paprika \\
    	2								& Bay Leaves \\
    	\unit[1]{lb}					& Cellentani Noodles \\
    	\unit[$\frac{1}{2}$]{lb}					& White cheddar cheese \\
    	\unit[$\frac{1}{4}$]{lb}		& Swiss cheese \\
    	\unit[$\frac{1}{4}$]{lb}		& Jarlsberg Cheese cheese \\
    	(1								& Habanero) \\
    	& Bread crumbs  \\
    }

    \preparation
    {%
    	\step Preheat oven to 350$^\circ$ F
    	\step Melt butter over medium-low heat in a medium sized dutch oven
    	\step Whisk in butter gradually, and heat until thick and smooth, about 1 minute. Make sure to whisk constantly, to prevent lumps.
    	\step Remove the roux from the heat, and whisk in the milk gradually
    	\step Return to the heat, and raise the heat to medium
    	\step Bring to a simmer, whisking constantly to keep smooth (about 15 minutes)
    	\step Simmer for about 5 minutes, until the sauce is thick and smooth
    	\step Add salt, pepper, and nutmeg to taste (I recommend about 1 tsp each)
    	\step Add sherry and chives
    	\step Add onions, paprika, bay leaves, and (optional) habanero
    	\step Bring to a simmer, and cook covered over low heat for 15 minutes, stirring occasionally
    	\step Meanwhile, cook cellentani according to package (recommend al dente)
    	\step Grate cheeses, and mix together in a large mixing bowl.
    	\step Add $\frac{2}{3}$ of the cheese to the sauce, and add salt and pepper to taste.
    	\step Drain the cellentani, and put in a large mixing bowl. Pour the cheese mixture over the noodles, and mix well.
    	\step Add half of the mixture to a 9'' $\times$ 13'' baking tray, then sprinkle half the remaining cheese on top.
    	\step Add the remaining mixture, top with the remaining cheese, and sprinkle over with bread crumbs.
    	\step Bake in the oven for 30 minutes. Let cool for 5 minutes before serving.
    }

\end{recipe}
