\documentclass[%
a4paper,
%twoside,
11pt
]{article}

% encoding, font, language
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}

\usepackage{nicefrac}

\usepackage[
    handwritten,
    nowarnings,
    %myconfig
]
{xcookybooky}

\usepackage{blindtext}    % only needed for generating test text

\definecolor{mygreen}{rgb}{0,.5,0}
\DeclareRobustCommand{\textcelcius}{\ensuremath{^{\circ}\mathrm{C}}}
\DeclareRobustCommand{\textfahr}{\ensuremath{^{\circ}\mathrm{F}}}

\setRecipeColors
{%
    recipename = mygreen,
    ing = blue,
    inghead = blue,
    prep,
    prephead,
    hint,
    hinthead,
}

\setHeadlines{
    inghead = Ingredients,
    prephead = Preparation,
    hinthead = Hint,
    calory = Calories,
    continuationhead = Continuation,
    continuationfoot = Continuation on next page,
    portionvalue = Portions
}

\setcounter{secnumdepth}{1}
\renewcommand*{\recipesection}[2][]
{%
    \subsection[#1]{#2}
}
\renewcommand{\subsectionmark}[1]
{% no implementation to display the section name instead
}


%%%%%%%%%%
% hyperref
\usepackage{hyperref}    % must be the last package
\hypersetup{%
    pdfauthor            = {Elias Szabo-Wexler},
    pdftitle             = {Elias's Cookbook},
    pdfsubject           = {Recipes},
    pdfkeywords          = {recipes},
    pdfstartview         = {FitV},
    pdfview              = {FitH},
    pdfpagemode          = {UseNone}, % Options; UseNone, UseOutlines
    bookmarksopen        = {true},
    pdfpagetransition    = {Glitter},
    colorlinks           = {true},
    linkcolor            = {black},
    urlcolor             = {black}
    citecolor            = {black},
    filecolor            = {black},
}
% hyperref
%%%%%%%%%%



\begin{document}

\title{Elias's Cookbook}
\author{Elias Szabo-Wexler}
\maketitle

\tableofcontents

\vspace{9em}

% background graphic
%\setBackgroundPicture[x, y=-2cm, width=\paperwidth-4cm, height, orientation = %pagecenter]
%{pic/background}


\input{Soups/Soups.tex}
\input{Beans/Beans.tex}
\input{Rice/Rice.tex}
\input{Pasta/Pasta.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     Salad
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Salads}
\begin{recipe}
[ %
    preparationtime = {\unit[25]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{4}},
    calory={1570},
]
{Strawberry and Spinach Salad}

    \graph
    {% pictures
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[2]{tb}              & Olive Oil\\
        \unit[1]{lb}              & Chicken Breast (skinned, boneless) \\
        \unit[5]{oz}              & Baby Spinach Leaves \\
        \unit[1]{lb}              & Strawberries, sliced \\
        \unit[4]{oz}              & Crumbled Feta Cheese \\
        1                         & Red Onion, sliced \\
        \unit[$\frac{1}{3}$]{cup} & Cranberry Raisins \\
        \unit[$\frac{1}{2}$]{cup} & Balsamic Vinaigrette \\
    }

    \preparation
    {%
        \step Heat olive oil over medium high heat in a skillet
        \step Combine spinach, strawberries, feta, cranberry raisins and red onion in a salad bowl
        \step Cook the chicken breasts whole over medium heat until cooked through, about 10 minutes
        \step Cut chicken into bite sized pieces, and add to salad
        \step Dress with Balsamic Vinaigrette, mix, and serve
    }

    \hint
    {%
        390 calories per bowl
    }

\end{recipe}
\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     Salad Dressing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Salad Dressings}
\begin{recipe}
[ %
    preparationtime = {\unit[5]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{1}},
    calory={540},
]
{Balsamic Vinaigrette}

    \graph
    {% pictures
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[$\frac{1}{4}$]{cup} & Balsamic Vinegar  \\
        \unit[$\frac{1}{4}$]{cup} & Olive Oil \\
        1                         & Clove Garlic, minced \\
        \unit[1]{pinch}           & Mustard, ground \\
        \unit[1]{pinch}           & Salt \\
        \unit[1]{pinch}           & Pepper  \\
    }

    \preparation
    {%
        \step Mix ingredients together and stir
    }

    \hint
    {%
        540 calories per $\frac{1}{2}$ cup (single serving)
    }

\end{recipe}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     Chicken
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Chicken}

\begin{recipe}
[ %
    preparationtime = {\unit[???]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{?}},
    calory={???},
]
{Tangy Chicken}

    \graph
    {% pictures%
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[2]{lb}              & Chicken breasts  \\
        \unit[1]{tb}              & Butter  \\
        \unit[1]{tb}              & Lemon Juice  \\
        \unit[2]{tb}              & Brown Sugar  \\
        \unit[$\frac{1}{2}$]{tsp} & paprika  \\
        \unit[$\frac{1}{2}$]{cup} & water  \\
        20						  & stuffed olives, sliced \\
        2						  & large onion \\
        Salt + pepper & \\
    }

    \preparation
    {%
    	\step Heat butter in a large sauce pan over medium-high heat, and cook the chicken.
    	\step Combine salt, pepper, paprika, brown sugar, lemon juice, onion, and water, and pour over meat
    	\step Sprinkle olives over the top
    	\step Cover, and simmer for 20 minutes
    }

\end{recipe}
\newpage

\begin{recipe}
[ %
    preparationtime = {\unit[???]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{4}},
    calory={???},
]
{Chicken with Balsamic Vinegar and Garlic}

    \graph
    {% pictures%
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[1]{lb}              & Chicken breasts  \\
        \unit[$\frac{3}{4}$]{lb}  & Mushrooms, sliced  \\
        1						  & Onion, diced \\
        \unit[2]{tb}              & Flour  \\
        \unit[2]{tb}              & Olive Oil  \\
        \unit[6]{cloves}          & garlic, minced  \\
        \unit[$\frac{1}{4}$]{cup} & Balsamic Vinegar  \\
        \unit[$\frac{3}{4}$]{cup} & Chicken Broth  \\
        2						  & Bay Leaves \\
        \unit[$\frac{1}{4}$]{tsp} & Dried Thyme (whole) \\
        \unit[1]{tb}              & Butter  \\
        & Salt \\ & pepper \\
    }

    \preparation
    {%
    	\step Combine flour, salt, and pepper in a small bowl, and dredge the chicken breast.
    	\step Heat the olive oil in a large saucepan over medium-high heat.
    	\step Saute the chicken until it is nicely browned on one side, without flipping (about 3 minutes).
    	\step Add the garlic, turn the chicken over, and scatter the mushrooms and onions over the chicken.
    	\step Continue frying, shaking the skillet, and stirring the mushrooms, for about 3 minutes.
    	\step Add vinegar, broth, thyme, and bay leaf. Cover tightly, and simmer over medium-low heat for 10 minutes, turning occasionally.
    	\step Remove the chicken to a plate, and continue simmering the sauce for 7 minutes over medium high heat.
    	\step Mix in the butter, discard the bay leaf, and add the chicken back to the sauce.
    	\step Let the chicken heat for several minutes, then serve hot.
    }

\hint{
This dish goes very well served over pasta (I particularly like penne pasta), with baked asparagus on the side. It's also extremely good when served with a white zinfandel, or other rose wine.
}

\end{recipe}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     Sides
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Side Dishes}
\begin{recipe}
[ %
    preparationtime = {\unit[15]{m}},
    bakingtime={\unit[12]{m}},
    bakingtemperature={\unit[400]{$^\circ$F}},
    portion = {\unit[4]{servings}},
    calory,
]
{Baked Asparagus}

    \graph
    {% pictures
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[1]{bunch} & Asparagus \\
        \unit[2]{tb}	& Olive Oil \\
        & salt \\
        & pepper \\
        & Parmesan cheese \\
    }

    \preparation
    {%
    	\step Preheat oven to 400$^\circ$F.
        \step Cut bottom 2'' off asparagus (removing tough base).
        \step Combine asparagus and olive oil in a large mixing bowl, and toss to coat.
        \step Place asparagus in a baking tray.
        \step Sprinkle with fresh grated salt, fresh grated pepper, and fresh grated Parmesan cheese.
        \step Bake for 12 minutes, until crispy.
        \step Serve hot!
    }

    \hint
    {%
        The asparagus will cool VERY quickly, so plan to have this be the last thing to finish!
    }

\end{recipe}
\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     Workouts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Workouts}
\begin{recipe}
[ %
    preparationtime = {\unit[5]{m}},
    bakingtime,
    bakingtemperature,
    portion = {\portion{1 (8 oz)}},
    calory={295},
]
{Preworkout Fruit Smoothie}

    \graph
    {% pictures
        %small=pic/glass,     % small picture
        %big=pic/ingredients  % big picture
    }

    \ingredients
    {%
        \unit[$\frac{1}{2}$]{cup} & Plain Yogurt (minimum sugar) \\
        \unit[$\frac{1}{2}$]{cup} & Water \\
        \unit[1]{cup} & Frozen Berries \\
        \unit[1]{handful} & Ice Cubes \\
        \unit[$\frac{1}{2}$]{cup} & Oats
    }

    \preparation
    {%
        \step Combine yogurt, water, frozen berries, ice cubes, and oats in blender
        \step Blend until smooth
    }

    \hint
    {%
        295 calories per 8 oz glass, $\approx 30g$ carbs
    }

\end{recipe}
\newpage

\end{document}
